Constant Partying: \\ Introducing a Generic Toolkit for Recursive Partitioning in R

### 2014-03-18 pkg/partykit/inst/NUS-2014/constparty.Rnw
cosmetics
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@499 255f4249-2263-4417-b1ea-8498779e27a7

We need a \textbf{partykit}!

@@

\textbf{Answer:} The R package \emph{partykit} provides unified
infrastructure for recursive partytioning, especially
\begin{itemize}
  \item representing fitted trees,
  \item printing trees,
  \item plotting trees,
  \item computing predictions from trees!
\end{itemize}

@@

\textbf{CART:} Apply \fct{rpart} to preprocessed \code{ttnc} data (see also below).

@@

\textbf{Software:} All examples have been produced with
R~\Sexpr{with(R.Version(), paste(major, minor, sep = "."))} and packages
partykit~\Sexpr{packageDescription("partykit")$Version},
rpart~\Sexpr{packageDescription("rpart")$Version},
RWeka~\Sexpr{packageDescription("RWeka")$Version},
evtree~\Sexpr{packageDescription("evtree")$Version}. All packages are
freely available under the GPL from \url{http://CRAN.R-project.org/}.

@@

\textbf{Data:} The contingency table \code{Titanic} is transformed
as explained in the \code{constparty} package vignette.

FIXME: Show code for completeness?

FIXME: Change/update/enhance references?

@@

Zeileis A, Hothorn T, Hornik K (2008).
 \dquote{Model-Based Recursive Partitioning.}
  \textit{Journal of Computational and Graphical Statistics},
  \textbf{17}(2), 492--514.
  \doi{10.1198/106186008X319331}

>>>>

We need a partykit!

@@

\textbf{Answer:} The R package partykit provides unified
infrastructure for recursive partytioning, especially
\begin{itemize}
  \item representing fitted trees,
  \item printing trees,
  \item plotting trees,
  \item computing predictions from trees!
\end{itemize}

@@

\textbf{CART:} Apply \fct{rpart} to preprocessed \code{ttnc} data (see \code{constparty} vignette in partykit).

@@

All examples have been produced with
R~\Sexpr{with(R.Version(), paste(major, minor, sep = "."))} and packages
\begin{itemize}
\item partykit~\Sexpr{packageDescription("partykit")$Version},
\item rpart~\Sexpr{packageDescription("rpart")$Version},
\item  RWeka~\Sexpr{packageDescription("RWeka")$Version},
\item evtree~\Sexpr{packageDescription("evtree")$Version}. 
\end{itemize}
All packages are
freely available under the GPL from \url{http://CRAN.R-project.org/}.

@@

@@
